Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-08 Ben_Manuscripts/structure_paper/Draft.tex
Edits, organization, renamings, figure additions

  %MRS5: want to get people engaged from the beginning. The first paragraph
  %should describe a problem to be solved. Then you can get into the motivating
  %details (like background of the alternatives, and why we need something
  %different).  I feel like this is an introduction into different types of
  %membranes, though it should be an introduction to the problem that this paper
  %takes steps towards solving.

  Figure S~\ref{S-fig:monomer_color_coded}

@@

%MRS6: I would keep a paragraph about here how current membranes DON'T
%work for this purpose. But one paragraph is enough.x

@@

%  Current commercial RO and NF membranes suffer from limitations inherent to
%  their fabrication. Although scalable, each of these two types of membranes has
%  a degree of stochasticity that makes overcoming the permeability-selectivity
%  tradeoff a challenge. Namely, it is difficult to increase the permeability of
%  a desired molecular or atomic species, while maintaining the same retention of
%  an undesired species \cite{werber_materials_2016}.

@@

  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} which can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike commercial NF membranes, LLC membrane pores
  are uniform in size. Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  %MRS6:
  described in this paper
  %chosen to make membranes for this application 
  are salts, and therefore lead to
  Donnan exclusion of ions in solution. The membrane gains a net surface charge
  when counterions from head groups that line the pore walls escape into the feed
  solution in order to balance the gradients of concentration and electric
  potential \cite{donnan_theory_1995}.

@@

  The H\textsubscript{II} phase pore geometry is 
%MRS6:
%better 
has a higher theoretical capacity
for transport than the
  Q\textsubscript{I} phase. The H\textsubscript{II} phase forms at room
  temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}).  The most
  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
  C when monomer is mixed with c.a.~20 wt\%
  glycerol\cite{carter_glycerol-based_2012}. Q\textsubscript{I} phase membranes
  consist of a tortuous network of three dimensionally interconnected pores that
  prevent optimal through-plane transport. The densely packed, non-tortuous and
  uniform sized pores of H\textsubscript{II} phase membranes represents the ideal
  geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed during self-assembly of NA-GA3C11 monomers, are
  isotropically aligned which is detrimental to membrane performance.

@@

%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
%  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
%  been revived in recent years. 
%  During early stages of exploration, hexagonal
%  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
%  macroscopically aligned, resulting in low flux membranes, and no clear route
%  towards scalable and economical filtration. 
%  For this reason, research efforts
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place
  \cite{feng_scalable_2014}. In 2016, Feng et al. showed that one could obtain
  the same result using a second technique termed soft confinement
  \cite{feng_thin_2016}. Current efforts are focused on extending the method to
  the H\textsubscript{II} phase and characterizing the performance of these newly
  aligned systems.

@@

  %BJC: Made my own version of the above, leaving out alignment details since it'

  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
  %           Thicken slabs
  %           Make pore region on slab (blue) bigger
  %           Bump up atom sizes in atomistic render
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

  Our current understanding of 
%MRS6:
the molecular details of
LLC membrane 
%systems 
nanostructure
is not 
%MRS6: 
%rich enough to be
sufficient
  able to precisely design them for specific separations. Over the past 20 years,
  H\textsubscript{II}-phase LLC polymer membrane studies have been limited
  primarily to Na-GA3C11 with some characterization done after minor structural
  modifications. Resel et al.~varied the length of the monomer tails and the
  counterion used and observed its affect on pore spacing
  \cite{resel_structural_2000}. In a later study of rejection performance, it was
  shown that membranes formed by cross-linked Na-GA3C11 in the
  H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in diameter
  because the pores are too large \cite{zhou_supported_2005}. We do not yet
  understand how to controllably reduce the effective pore size or how to tune
  the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. It will be
  challenging to efficiently narrow down the large design space in a laboratory
  setting without a robust model.

  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which will be crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations will provide the required level of detail
  (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential

  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

@@

  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
%MRS6: this is one place where I might go to passive voice, since anyone can only speculate not just us.  
  \caption{We can only speculate about solute behavior inside the membrane
	  pores based on our previous picture of the pore structure (a). 
%MRS6: should be present text, not ``will use'' since it's what's happening in this paper. Look for this throughout.
          We will use a
	  detailed molecular model in order to appropriately model the pore's complex
	  architecture which is crucial to understanding the mechanism of solute
	  transport (b). The head group region is colored blue
%MRS6: probably mention from actual simulations we will describe below.
	  and the tail region is colored cyan in both representations.}~\label{fig:detail}
  \end{figure}

  Here we develop a model of the Col\textsubscript{h} assembly formed by
  Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which will allow us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns which are useful for reconstructing structural data.
  We anticipate using this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

  In order to appropriately model transport in these ordered, nanoporous
  organic systems, we must first gain a thorough understanding of the nanoscopic
  structure of LLC polymer membranes. Our current level of understanding about
  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
  we can infer that monomers aggregate into hexagonally packed columns with their
  head groups facing towards the column center. There remain several key questions
  that we will investigate in order to expand this understanding:

%BJC3: reworded a lot of these to be more in line with Matt's way of thinking about LC systems
%MRS6: formatting suggestion
%  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
  A simple molecular simulation study of a similar molecule suggested that
  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
  Their model likely does not sufficiently imitate the chemical environment present
  in the real system since it only contains 16 total monomers. A separate calculation
  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
  proposes that each pore is surrounded by seven
  monomers\cite{resel_structural_2000}. Our best chance to answer this question
  is by using a molecular model orders of magnitude larger than any other
  reported atomistic liquid crystal membrane simulation, as we present here. We
  will directly change the density of monomers in each pore and note its effect
  on membrane structure.

%  \item \textit{How do monomers in each layer position themselves with respect to
%  surrounding layers? \label{point:orientation}}
  \item \textit{In what orientation do monomer head groups stack on top of each
  other \label{point:orientation} 
  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
  attraction which favors the parallel displaced configuration in all cases except
  where the substitutions are extremely electron withdrawing  
  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
  configuration due to its geometric incompatibility with a hexagonal columnar phase.
  The entropic contribution of the long alkane tails should overwhelm any attraction
  between aromatic head groups in the T orientation. We limit our studies to
  comparison of systems built in the parallel displaced and sandwiched configurations.

%  \item \textit{Does our model support the existence of layers and if so, how well
%  defined are the layers? \label{point:layers}}
%  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
%  perpendicular to the membrane plane, combined with the wedge-like character of
%  the LLC monomers, suggests that monomers should arrange into disks that stack in
%  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
%  monomer head groups which leaves no description of what is happening in the
%  monomer tail region. The tails may entangle isotropically while maintaining
%  stacking order among headgroups.  
% BJC3:rephrasing everything about the above question. 
  \item \textit{How strong are stacking correlations between monomer head groups?
  \label{point:layers}}

  \item \textit{What constitutes a pore, and what are the details of its composition?
  \label{point:poredefinition}}
  The limited picture that experiment provides tells us that there are
  hexagonally packed, hydrophilic regions where transport is likely to occur.
  One may instinctively assume that these regions are hollow tube-like pathways.
  We will explore the composition of the pores and the partition between the
  hydrophilic and hydrophobic regions.

  \item \textit{Is it necessary to include any water in order to appropriately model
  the Col\textsubscript{h} phase? \label{point:water}}
  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
  it has been suggested by experimentalists, in
  unpublished communications, that it is likely that neat monomer leaches small
  amounts of ambient water. Experimentally, achieving a hexagonal phase with a
  completely dry system has proven difficult. If neat monomer sits in ambient
  conditions, its color turns from transparent to slightly opaque and a hexagonal
  phase forms. Although we will not explore whether water is necessary for
  self-assembly, we hypothesize that the hydrogen bonding network formed by the
  water may play a role in structuring the pores and holding together the
  hexagonal phase. We can look at correlation functions and use simulated X-ray
  diffraction patterns to see if there is any meaningful structural difference
  between a ``dry'' and ``wet'' system.

  We used experimental small-angle X-ray scattering (SAXS) data from
  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
  since it encodes all structural details down to the sub-nm scale.  There are
  five major features of interest present in the 2D experimental pattern shown in
  Figure \ref{fig:WAXS}.

@@

	\item \textit{R-helix}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
	space periodic spacing of 7.4 \AA~. This reflection has been interpreted as
	2\textsubscript{1} helical ordering of aromatic rings along the z axis
	\cite{feng_scalable_2014}, meaning that if one traces the positions of the
	aromatic rings with a helical curve, then for each full turn in the helix, one
	will encounter two aromatic rings. For this reason we will refer to reflection
	as R-helix.

@@

  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
%BJC: What do you think of the labels now? I tried to make it more clear what each label refers
% to graphically. I can't decide if it's too cluttered. An alternative is to number them as  
% I had them before, and then define them in a little box inset to the figure
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-helix) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

@@

  \subsubsection{\textit{Determining equilibration time}}

  \subsubsection{\textit{Calculation of pore spacing}}

  To calculate the equilibrated pore spacing, we measured the distance between
  pore centers. We located the pore centers by averaging the coordinates of sodium
  ions in their respective pores. We generated pore spacing statistics 
  using the bootstrapping technique (See Supporting Information).

  \subsubsection{\textit{The nematic order parameter}}

>>>>

  % BJC5: Note to self -- how to use latex xr : Figure S~\ref{S-fig:monomer_color_coded}

@@

@@

% MRS6: I would keep a paragraph about here how current membranes DON'T
% work for this purpose. But one paragraph is enough.
% BJC5: added back below paragraph
  Current commercial RO and NF membranes suffer limitations to there selectivity 
  which is inherent to their fabrication. Although scalable, each of these two types
  of membranes has a degree of stochasticity that makes overcoming well-known the 
  permeability-selectivity tradeoff a challenge. Namely, it is difficult to increase
  the permeability of a desired molecular or atomic species, while maintaining the same 
  retention of an undesired species \cite{werber_materials_2016}.

@@

  Crosslinked lyotropic liquid crystal (LLC) membranes may be capable of
  performing highly selective separations. LLCs are amphiphilic molecules that
  have the ability to self-assemble into porous nanostructures
  \cite{smith_ordered_1997} which can be crosslinked to create mechanically
  strong membrane films with pores on the order of 1 nm in diameter
  \cite{zhou_supported_2005}. Unlike most commercial NF membranes, LLC membrane pores
  are uniform in size. Since LLC membranes lack a pore size distribution, they
  inherently exhibit high selectivity due to their strict molecular weight
  cut-off (MWCO)~\cite{zhou_supported_2005}. Additionally, the LLC monomers
  described in this paper are salts, and therefore lead to Donnan exclusion of ions
  in solution. The membrane gains a net surface charge when counterions from the head
  groups that line the pore walls escape into the feed solution in order to balance 
  the gradients of concentration and electric potential \cite{donnan_theory_1995}.

@@

  The H\textsubscript{II} phase pore geometry is has a higher theoretical capacity
  for transport than the Q\textsubscript{I} phase. The H\textsubscript{II} phase forms
  at room temperature in the presence of c.a.~10 wt\% water and consists of hexagonally
  packed, hydrophilic pore columns\cite{smith_ordered_1997}. In the absence of
  water, neat monomer will form the same hexagonal columnar structure which, in
  literature, has been referred to as the Col\textsubscript{h} thermotropic
  phase\cite{feng_scalable_2014} (See Figure~\ref{fig:hII_phase}). The most
  promising Q\textsubscript{I} phase for membrane applications forms at 70\degree
  C when monomer is mixed with c.a.~20 wt\% glycerol\cite{carter_glycerol-based_2012}.
  Q\textsubscript{I} phase membranes consist of a tortuous network of three dimensionally 
  interconnected pores that prevent optimal through-plane transport. The densely packed, 
  non-tortuous and uniform sized pores of H\textsubscript{II} phase membranes represent
  the ideal geometry for achieving high solute flux\cite{matyka_tortuosity-porosity_2008}.
  Despite the promise of the H\textsubscript{II} phase, the hexagonally packed
  liquid crystalline domains, formed when Na-GA3C11 monomers self-assemble, are
  isotropically aligned which is detrimental to membrane permeability.

@@

%  Research into the H\textsubscript{II} phase of polymerized LLC membranes has
%  been revived in recent years. 
%  During early stages of exploration, hexagonal
%  mesophases formed by Na-GA3C11 (Figure~\ref{fig:assembly}) could not be
%  macroscopically aligned, resulting in low flux membranes, and no clear route
%  towards scalable and economical filtration. 
%  For this reason, research efforts

%MRS5: not a strong thesis.  Why has it been revived?  The reasons for that would be a better thesis.
  Recently, researchers have learned how to macroscopically align the hexagonal
  domains which has revived research into H\textsubscript{II} phase LLC membranes.
  Previously, research efforts were focused on the Q\textsubscript{I} phase,
  whose geometry does not require alignment. In 2014, Feng et al.~showed that one
  can align Col\textsubscript{h} hexagonal domains using a magnetic field with
  subsequent cross-linking to lock the structure in place\cite{feng_scalable_2014}.
  In 2016, Feng et al. showed that one could obtain the same result using a second
  technique termed soft confinement\cite{feng_thin_2016}. Current efforts are focused
  on extending the method to the H\textsubscript{II} phase and characterizing the 
  performance of these newly aligned systems.

@@

% BJC5 : This is how it is described in Xunda's papers. Should I shift to something
% that doesn't rely on stacked disks? Maybe illustrate monomers stacked into
% columns instead?
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_thick.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The LLC monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnar mesophases (e).}~\label{fig:assembly}
  \end{figure}

  Our current understanding of the molecular details of LLC membrane nanostructure
  is not sufficient to be able to precisely design them for specific separations. 
  Over the past 20 years, H\textsubscript{II}-phase LLC polymer membrane studies have
  been limited primarily to Na-GA3C11 with some characterization done after minor 
  structural modifications. Resel et al.~varied the length of the monomer tails and the
  counterion used and observed its affect on pore spacing \cite{resel_structural_2000}.
  In a later study of rejection performance, it was shown that membranes formed by cross-
  linked Na-GA3C11 in the H\textsubscript{II} phase cannot separate solutes less than 1.2 
  nm in diameter because the pores are too large \cite{zhou_supported_2005}. We do not
  yet understand how to controllably reduce the effective pore size or how to tune
  the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. It will be
  challenging to efficiently narrow down the large design space in a laboratory
  setting without a robust model.

  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which will be crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations will provide the required level of detail
  (Fig. \ref{fig:detail}), assuming the force fields are sufficiently accurate.
  With such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can observe how the choice of
  head group interacts with solutes of interest. We can interchange
  counterions which may influence both the pore size and the strength of the
  Donnan potential. 
  %which affects the degree to which the membrane can exclude
  %charged species at the membrane surface.

@@

  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{One can only speculate about solute behavior inside the membrane
	  pores based on the previously established picture of the pore structure (a). 
      We use a detailed molecular model in order to appropriately model the pore's
      complex architecture which is crucial to understanding the mechanism of solute
	  transport (b). The head group region is colored blue and the tail region is
	  colored cyan in both representations. This image was generated from the molecular
	  simulations run for this paper.}~\label{fig:detail}
  \end{figure}

  Here we develop a molecular model of the Col\textsubscript{h} assembly formed by
  Na-GA3C11. Compared to the H\textsubscript{II} phase, the Col\textsubscript{h}
  phase is a simpler starting point. The system has no water which will allow us
  to simulate longer timescales, and there exists detailed experimental
  characterization of the fully aligned state, including 2D wide-angle X-ray
  scattering (WAXS) patterns (Figure\ref{fig:WAXS}) which are useful for reconstructing 
  structural data. We will use this Col\textsubscript{h} model in order to build an 
  H\textsubscript{II} model in the future.
  %The two phases appear to share similar structural characteristics since the
  %pore spacings in each system are in close agreement
  %\cite{feng_thin_2016,resel_structural_2000}.

%  We used experimental small-angle X-ray scattering (SAXS) data from
%  \cite{feng_thin_2016} (Fig.~\ref{fig:SAXS}) and wide angle X-ray scattering
%  (WAXS) data (Fig.~\ref{fig:WAXS}, produced as described in
%  \cite{feng_scalable_2014}) for comparison to our model. We rely primarily on the 2D WAXS data
%  since it encodes all structural details down to the sub-nm scale.  
  There are five major features of interest present in the 2D experimental pattern shown 
  in Figure \ref{fig:WAXS}.

@@

	\item \textit{R-double}: A weak intensity line, located at exactly half
	the $q_z$ value of R-$\pi$ ($q_z$ = 0.85 \AA$^{-1}$), corresponds to a real
	space periodic spacing of 7.4 \AA~. Since this reflection corresponds to double
	the spacing of R-$\pi$ in real space, will refer to this reflection as R-double. 
	R-double has been interpreted as 2\textsubscript{1} helical ordering of aromatic
	rings along the z axis\cite{feng_scalable_2014}, meaning that if one traces the 
	positions of the aromatic rings with a helical curve, then for each full turn 
	in the helix, one will encounter two aromatic rings.

@@

  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) (Reproduced from \cite{feng_thin_2016}) The repeat spacing
		in the 1D small angle X-ray scattering pattern is characteristic of hexagonal
		packing. The leading peak, q*, represents the distance between the
		d\textsubscript{100} planes. Using this distance, we know that the distance
		between pore centers is 4.12 nm. (b) 2D WAXS gives
		details about repeating features on the order of angstroms. Experimentalists
		have explained each of the 5 major reflections present as follows: (R-$\pi$) Aromatic
		head groups $\pi-\pi$ stack 3.7 \AA~apart. (R-double) Monomers arrange vertically in
		a 2\textsubscript{1} helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots)
		Monomer tails are tilted with respect to the membrane plane. (V) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally}
	\label{fig:SWAXS}
 \end{figure}

  Despite having structural data, there is still information which experiment cannot
  definitively answer. There are a number of structural questions we wish to answer in this 
  article. We want to know:
  \begin{enumerate}
    \item What is the density of monomers that pack around each hydrophilic core? 
    \label{point:monomernum}

 	Authors often describe this and similar systems as being made up of layers. A simple
 	molecular simulation study of a similar molecule suggested that there are 4 monomers
 	in each layer. Their estimation is based on a simulated system containing only 16 total
 	monomers which likely does not sufficiently model the chemical environment present in
 	the real system.~\cite{zhu_methacrylated_2006}. A separate calculation based on the 
 	volume of the liquid crystal monomers proposes that there are seven monomers in each 
 	layer~\cite{resel_structural_2000}.

 	We are careful to avoid the term 'layers' since a liquid crystalline system has, by 
 	definition, long range order in 1 or 2 spatial dimensions and short range order in 	
 	the other dimensions.~\cite{chaikin_principles_1995}  % page 58
 	In the system we are studying, there are long-range 2D correlations in the 
 	hexagonal array of pores (xy plane) and short range correlations in the z-direction.
 	We will use our atomistic molecular model to study how the system's structure is 
 	effected by the density of monomers surrounding each pore's hydrophilic core.

	\item What structural motif best matches experimental 2D WAXS patterns?\label{point:xrdmatch}

	On the short timescales accessible to MD, we observe distinct metastable configurations
	which depend on starting configuration. We simulated XRD patterns of our system and 
	compared them to experimental 2D WAXS patterns (Figure~\ref{fig:WAXS} so that we ensure our
	model creates a nanoscopic chemical environment maximally consistent with experiment within 
	the constraints	of our forcefield. Using this approach, we are able to confirm some previous
	interpretations	of the WAXS pattern and refute others.

	%BJC5: I could add brief references to other LLC studies which look at hexagnoal phase, but
	% without scrutinizing the structural details. In other words, other authors have gotten 
	% hexagonal phases with self-assembly, but they can't prove that their structure is the same
	% as experiment. The best there are, are 1D structure factors in the small angle regime.

	\item What is the chemical composition of the pores?\label{point:composition}

	The limited picture that experiment provides tells us that there are hexagonally packed, 
	hydrophilic regions where transport is likely to occur. One may instinctively imagine these 
	regions as tube-like pathways with well-defined boundaries. We will explore the composition
	of the pores, the partition between the hydrophilic and hydrophobic regions, and its 
	sensitivity to initial configuration.

    \item Is it necessary to include any water in order to appropriately model the 
    Col\textsubscript{h} phase? \label{point:water}

	While the Col\textsubscript{h} phase is described as dry, it is likely that small amounts of
	ambient water may be leached into the system. The hydrogen bonding network formed by the 
	water may play a role in structuring the pore. We used simulated X-ray diffraction patterns
	to see if there is any meaningful structural difference between a "dry" and "wet" system.

%  In order to appropriately model transport in these ordered, nanoporous
%  organic systems, we must first gain a thorough understanding of the nanoscopic
%  structure of LLC polymer membranes. Our current level of understanding about
%  the structure at the nanoscale is limited. Using X-ray diffraction and TEM data
%  we can infer that monomers aggregate into hexagonally packed columns with their
%  head groups facing towards the column center. There remain several key questions
%  that we will investigate in order to expand this understanding: 
%
%  \begin{enumerate}

%BJC3: reworded a lot of these to be more in line with Matt's way of thinking about LC systems
%MRS6: formatting suggestion
%  \item \textit{If layers do exist, how many monomers constitute a single layer? \label{point:monomernum}} 
%  \item \textit{How many monomers pack around a single pore column?\label{point:monomernum}} 
%  A simple molecular simulation study of a similar molecule suggested that
%  4 monomers radially pack around hydrophilic pore columns \cite{zhu_methacrylated_2006}.
%  Their model likely does not sufficiently imitate the chemical environment present
%  in the real system since it only contains 16 total monomers. A separate calculation
%  for NA-GA3C11, based on the estimated volume of the liquid crystal monomers,
%  proposes that each pore is surrounded by seven
%  monomers\cite{resel_structural_2000}. Our best chance to answer this question
%  is by using a molecular model orders of magnitude larger than any other
%  reported atomistic liquid crystal membrane simulation, as we present here. We
%  will directly change the density of monomers in each pore and note its effect
%  on membrane structure.
%
%%  \item \textit{How do monomers in each layer position themselves with respect to
%%  surrounding layers? \label{point:orientation}}
%  \item \textit{In what orientation do monomer head groups stack on top of each
%  other \label{point:orientation} 
%  $\pi$-$\pi$ stacking interactions between aromatic monomer head groups may be
%  a driving force of self-assembly in this system \cite{gazit_possible_2002}. Gas
%  phase \textit{ab initio} studies of benzene dimers have shown a clear energetic
%  advantage for parallel displaced and T-shaped $\pi$-$\pi$ stacking
%  conformations over a sandwiched conformation \cite{sinnokrot_estimates_2002}.
%  Substituted benzene rings exhibit an even stronger $\pi$-$\pi$ stacking
%  attraction which favors the parallel displaced configuration in all cases except
%  where the substitutions are extremely electron withdrawing  
%  \cite{waller_hybrid_2006,ringer_effect_2006}. We did not consider the T-shaped 
%  configuration due to its geometric incompatibility with a hexagonal columnar phase.
%  The entropic contribution of the long alkane tails should overwhelm any attraction
%  between aromatic head groups in the T orientation. We limit our studies to
%  comparison of systems built in the parallel displaced and sandwiched configurations.

%  \item \textit{Does our model support the existence of layers and if so, how well
%  defined are the layers? \label{point:layers}}
%  Indications of strong $\pi$-$\pi$ stacking interactions in the direction
%  perpendicular to the membrane plane, combined with the wedge-like character of
%  the LLC monomers, suggests that monomers should arrange into disks that stack in
%  layers. $\pi$-$\pi$ stacking will only occur between the aromatic
%  monomer head groups which leaves no description of what is happening in the
%  monomer tail region. The tails may entangle isotropically while maintaining
%  stacking order among headgroups.  
% BJC3:rephrasing everything about the above question. 
%  \item \textit{How strong are stacking correlations between monomer head groups?
%  \label{point:layers}}

%  \item \textit{What constitutes a pore, and what are the details of its composition?
%  \label{point:poredefinition}}
%  The limited picture that experiment provides tells us that there are
%  hexagonally packed, hydrophilic regions where transport is likely to occur.
%  One may instinctively assume that these regions are hollow tube-like pathways.
%  We will explore the composition of the pores and the partition between the
%  hydrophilic and hydrophobic regions. 
% 
%
%  \item \textit{Is it necessary to include any water in order to appropriately model
%  the Col\textsubscript{h} phase? \label{point:water}}
%  While past work describes the Col\textsubscript{h} phase as dry~\cite{feng_scalable_2014}, 
%  it has been suggested by experimentalists, in
%  unpublished communications, that it is likely that neat monomer leaches small
%  amounts of ambient water. Experimentally, achieving a hexagonal phase with a
%  completely dry system has proven difficult. If neat monomer sits in ambient
%  conditions, its color turns from transparent to slightly opaque and a hexagonal
%  phase forms. Although we will not explore whether water is necessary for
%  self-assembly, we hypothesize that the hydrogen bonding network formed by the
%  water may play a role in structuring the pores and holding together the
%  hexagonal phase. We can look at correlation functions and use simulated X-ray
%  diffraction patterns to see if there is any meaningful structural difference
%  between a ``dry'' and ``wet'' system.
%
%  \end{enumerate}

@@
